Numerical simulation of the dynamics of the artificial heart valve

### 2015-05-09 citech-2015/Paper-template/paper.tex
Working on the text for citech paper

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

@@

\begin{figure}
\centering
\includegraphics[height=6.2cm]{images/aorta_scheme.png}
\caption{Aortic valve and its location inside heart}
\label{fig:aortic_valve_example}
\end{figure}

>>>>

\usepackage{amssymb, amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

@@

\begin{figure}
\centering
\includegraphics[height=6.2cm]{images/aorta_scheme_gray.png}
\caption{Aortic valve and its location inside heart}
\label{fig:aortic_valve_example}
\end{figure}

We model the blood as a viscous incompressible inhomogeneous two component fluid with variable viscosity, and vessel wall and valve leaflets as a
liquid impermeable surface with specified stiffness. Vessel and valve leaflets are deformed by a fluid pressure.

\begin{figure}
\centering
\includegraphics[width=12.5cm]{images/area_3d.png}
\caption{Scheme of the boundaries of the computational domain}
\label{fig:area_3d}
\end{figure}

Because the source of the blood motion in vessels is the pressure during the cardiac cycle, we will describe the problem of the blood flow
by the following nonstationary system of differential equations of Navier-Stokes \cite{gummel}:

\begin{gather}
    \label{eq:navier_stokes:motion}
    \frac{\partial \vec{u}}{\partial t} + (\vec{u} \cdot \nabla) \vec{u} = - \frac{1}{\rho} \nabla p + \nabla \sigma + \vec{f}\\
    \label{eq:navier_stokes:continuity}
    \frac{\partial \rho}{\partial t} + \nabla \cdot (\rho \vec{u}) = 0 
\end{gather}

with the initial and boundary conditions:

\begin{gather}
    \label{eq:navier_stokes:velocity_conditions}
    \vec{u}(\bar{x}, 0) = \vec{u}_0 \qquad \vec{u}|_{\Gamma_1, \Gamma_4} = \vec{u}_b \qquad u_{\Gamma_2, \Gamma3} = 0\\
    \label{eq:navier_stokes:pressure_conditions}
    p_{\Gamma_2} = p_{in} \qquad p_{\Gamma_3} = p_{out}
\end{gather}

where $\bar{x}=(x,y,z) \in \Omega$, $\vec{u}=(u,v,w)$ - velocity vector, $\vec{u}_b$ - velocity of the vessel wall and valve leaflet motion during the deformation,
$\rho=\rho(\bar{x}, t)$ - density, $p=p(\bar{x}, t)$ - pressure, $\sigma = \mu (\nabla \vec{u} + (\nabla \vec{u})^T)$ - viscous stress tensor,
$\mu = \mu(\bar{x}, t)$ - viscosity of fluid, $\vec{f} = \vec{f}(\bar{x}, t)$ - vector of body forces, which is futher used to determine form of the vessel and valve leaflets.
